Delayed effects of [responses to?] climate lead to demographic divergence in a fragmented Amazonian landscape

### 2021-04-30 doc/paper.Rmd
fixed a couple typos in statistics

Drought history also had a significant effect on plant size in both habitats (p \< 0.001).
The fitted crossbasis functions for fragments and continuous forest showed somewhat similar patterns, although the surface for 1-ha fragments was much more complex (edf = 17.9 for 1-ha fragments; edf = 5.9 for continuous forest; see also Figure \@ref(fig:growth-spei)).
Drought at lags 8--11 (March - June, the end of the wet season) increase growth in both habitats, but more strongly in 1-ha fragments.

@@

FInally, with the exception of growth in 1-ha fragments (p = 0.257), the delayed effects of SPEI on all three vital rates varied significantly between plots (p \< 0.001 for the random effect of plot).

>>>>

Drought history also had a significant effect on plant size in both habitats (p \< 0.001).
The fitted crossbasis functions for fragments and continuous forest showed somewhat similar patterns, although the surface for 1-ha fragments was much more complex (edf = 17.9 for 1-ha fragments; edf = 13.1 for continuous forest; see also Figure \@ref(fig:growth-spei)).
Drought at lags 8--11 (March--June, the end of the wet season) increase growth in both habitats, but more strongly in 1-ha fragments.

@@

FInally, with the exception of survival in 1-ha fragments (p = 0.257), the delayed effects of SPEI on all three vital rates varied significantly between plots (p \< 0.001 for the random effect of plot).
